### 2014-09-18 paper.tex
removed reads_error_profiles_legend.pdf
minor revised paper.tex

updated cdf figure

\caption{
\bf{Unique regions from global and local assembly}}
\begin{tabular}{ccccc}
\hline
Dataset & \multicolumn{2}{c}{Unique Region} & \multicolumn{2}{c}{Matched with mouse proteins}\\
 & Global & Local & Global & Local\\
\hline
Line 6 uninfected & 1285929 & 96830 & 260321 (20.0\%) & 9413 (9.7\%)\\
Line 6 infected & 1631356 & 59813 & 312849 (19.2\%)& 5132 (8.6\%)\\
Line 7 uninfected & 1800634 & 104229 & 349346 (19.4\%) & 9883 (9.5\%)\\
Line 7 infected & 1611354 & 125640 & 296915 (18.4\%)& 9381 (7.5\%)\\
\hline
%table information
\end{tabular}
%\begin{flushleft}Table Caption
%\end{flushleft}
\label{unique_sequences_matched_mouse}

@@

\caption{
\bf{Number of putative genes and isoforms}}
\begin{tabular}{cccccc}
\hline
Method& Gene & Isoform \\ 
\hline
Ensembl & 17,934 & 23,392 \\
Global & 21,492 & 31,418 \\
Local & 24,928 & 29,776 \\
Global + Local & 22,587 & 34,800 \\
Cufflinks & 31,073 & 38,307 \\
Global + Local + Cufflinks & 25044 & 45793 \\
Global + Local + Cufflinks (w/Ensembl) & 24915 & 60976 \\
\hline
%table information
\end{tabular}
%\begin{flushleft}\footnotesize \textit{*Minumum set}
%\end{flushleft}
\label{genes_transcripts}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{cdf_splice.pdf}
\end{center}
\caption{
{\bf Cumulative counts of splice junctions with spliced reads from both single-
and paired-end data.}
}
\label{cdf_splice}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{chick_venn.pdf}
\end{center}
\caption{
{\bf Splice sites in chicken Ensembl gene models detected by Cufflinks and the
{\em de novo} assembly pipeline.} Cufflinks detects many annotated isoforms
that are not detected by the pipeline.  The figure also shows that both methods
detect a large number of unannotated splice junctions, which suggests that those
junctions may be genuine.  }
\label{chick_venn}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{mouse_venn.pdf}
\end{center}
\caption{
{\bf Splice sites in mouse Ensembl gene models, Cufflinks and the \emph{de novo}
assembly pipeline.} In contrast to chicken datasets, Cufflinks and the pipeline
detects the similar amount of non-overlapped annotated junctions.  This may due
to a higher quality of gene annotations in mouse.  }
\label{mus_venn}
\end{figure}

>>>>

\caption{
\bf{Unique regions from global and local assembly}}
\begin{tabular}{ccccc}
\hline
Dataset & \multicolumn{2}{c}{Unique Region} & \multicolumn{2}{c}{Matched with mouse proteins}\\
 & Global & Local & Global & Local\\
\hline
Line 6 uninfected & 1,285,929 & 96,830 & 260,321 (20.0\%) & 9,413 (9.7\%)\\
Line 6 infected & 1,631,356 & 59,813 & 312,849 (19.2\%)& 5,132 (8.6\%)\\
Line 7 uninfected & 1,800,634 & 104,229 & 349,346 (19.4\%) & 9,883 (9.5\%)\\
Line 7 infected & 1,611,354 & 125,640 & 296,915 (18.4\%)& 9,381 (7.5\%)\\
\hline
%table information
\end{tabular}
%\begin{flushleft}Table Caption
%\end{flushleft}
\label{unique_sequences_matched_mouse}

@@

\caption{
\bf{Number of putative genes and isoforms}}
\begin{tabular}{cccccc}
\hline
Method& Gene & Isoform \\ 
\hline
Ensembl & 17,934 & 23,392 \\
Global & 21,492 & 31,418 \\
Local & 24,928 & 29,776 \\
Global + Local & 22,587 & 34,800 \\
Cufflinks & 31,073 & 38,307 \\
Global + Local + Cufflinks & 25,044 & 45,793 \\
Global + Local + Cufflinks (w/Ensembl) & 24,915 & 60,976 \\
\hline
%table information
\end{tabular}
%\begin{flushleft}\footnotesize \textit{*Minumum set}
%\end{flushleft}
\label{genes_transcripts}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{cdf_splice.pdf}
\end{center}
\caption{
{\bf Cumulative counts of splice junctions with spliced reads from single- and
paired-end data.}
}
\label{cdf_splice}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{chick_venn.pdf}
\end{center}
\caption{
{\bf Splice sites in chicken Ensembl gene models detected by Cufflinks and the
{\em de novo} assembly pipeline.} Cufflinks detects many annotated isoforms
that are not detected by the pipeline.  The figure also shows that both methods
detect a large number of unannotated splice junctions.}
\label{chick_venn}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=5in]{mouse_venn.pdf}
\end{center}
\caption{
{\bf Splice sites in mouse Ensembl gene models, Cufflinks and the \emph{de novo}
assembly pipeline.} In contrast to chicken datasets, Cufflinks and the pipeline
detects the similar amount of non-overlapped annotated junctions.}
\label{mus_venn}
\end{figure}
